---
title: "Literature Review"
author: "Xinyi Lin"
date: "12/7/2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE,
  warning = FALSE)

library(tidyverse)
library(caret)
```

### Load Main dataset

```{r}
cancer_reg = read_csv("./data/Cancer_Registry.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(target_death_rate, everything()) %>%
  separate(geography, into = c("county", "state"), sep = ", ") %>% 
  mutate(
    avg_deaths_per_year = as.numeric(avg_deaths_per_year),
    med_income = as.numeric(med_income),
    pop_est2015 = as.numeric(med_income),
    county = str_replace(county, " ", ""),
    log_med_income = log(med_income))
```

### Add Smoking Pravalence (current/previous smokers)

* Lung cancer account for highest proportion of cancer deaths. ~20% of lung cancer patients have never smoked. Smoking prevalence within a state is important indicator for mortality. 
```{r}
tobacco_2013 = read_csv(file = "./data/BRFD_tobacco_2010_present.csv") %>% 
  janitor::clean_names() %>% 
  filter(response == "Never", year == "2013", gender == "Overall") %>% 
  dplyr::select(year = "year", state = "location_desc", response, percent_never = "data_value") %>%
  mutate(
    percent_smoke = as.numeric(100 - percent_never),
    year = as.numeric(year)) %>% 
  dplyr::select(state, percent_smoke) %>% 
  filter(state != c("Guam", "National Median (States and DC)", "Puerto Rico"))

# join data on smoking prevalence by state
cancer_reg = left_join(cancer_reg, tobacco_2013, by = "state") %>% 
  dplyr::select(target_death_rate, state, county, percent_smoke, everything())

# smoking prevalence for 50 states and district of columbia
cancer_reg %>% 
  distinct(state, percent_smoke)
```

### Model Building, Based on Subset

```{r}
# select(-county, -state) %>%
# variables based on tidying steps
cancer_reg = cancer_reg %>% 
  mutate(mortality = avg_deaths_per_year/pop_est2015, prevalence = avg_ann_count/pop_est2015) %>%
  dplyr::select(-pop_est2015, -avg_ann_count, -avg_deaths_per_year) %>%
  mutate(study_per_cap =  
        as.factor(ifelse(study_per_cap == 0, "none", 
                         ifelse(study_per_cap < quantile(study_per_cap, .25), "low",
                         ifelse(study_per_cap < quantile(study_per_cap, .5), "medium" ,
                         ifelse(study_per_cap < quantile(study_per_cap, .75), "high", "very high")))))) %>%
  mutate(pct_non_white = pct_black+ pct_asian + pct_other_race) %>%
  dplyr::select(-pct_black, -pct_asian, -pct_other_race)

# subset based on Apoorva's selection & smoke variable
# remove state & county
cancer_reg_subset = cancer_reg %>%
  dplyr::select(
    target_death_rate, percent_smoke, incidence_rate, med_income, median_age_male, median_age_female, pct_hs18_24,
    pct_bach_deg25_over, pct_employed16_over, pct_unemployed16_over, pct_public_coverage_alone, birth_rate, mortality, prevalence,
    pct_private_coverage, pct_emp_priv_coverage, pct_public_coverage)
```

### Final Model Recommend

stepwise model: 
target_death_rate ~ incidence_rate + med_income + median_age_male + median_age_female + pct_hs18_24 + pct_hs25_over + pct_bach_deg25_over + pct_employed16_over + pct_unemployed16_over + pct_private_coverage +  pct_emp_priv_coverage + pct_public_coverage + pct_public_coverage_alone + pct_white + birth_rate + mortality + prevalence

17 parameter model minimizes Cp, while 21 parameter model minimizes adjR2.




Adjusted R-squared:  0.4935

**4 predictor model:** target_death_rate ~ log(pct_bach_deg25_over), incidence_rate, pct_private_coverage, percent_smoke

```{r}
fit_parsimony = lm(target_death_rate ~ log(pct_bach_deg25_over) + incidence_rate + pct_private_coverage + 
    percent_smoke, data = cancer_reg_subset)

summary(fit_parsimony)
```

### 10-fold cv

```{r}
train_data_10 = trainControl(method = "cv", number = 10)

# Fit the 4-variables model that we discussed in previous lectures
model_caret_10 = 
  train(target_death_rate ~ log(pct_bach_deg25_over) + incidence_rate + pct_private_coverage + 
    percent_smoke, 
    data = cancer_reg_subset,
    trControl = train_data_10,
    method = 'lm',
    na.action = na.pass)

model_caret_10
```

```{r}
# Model coefficients

model_caret_10$finalModel

# Results of each fold

model_caret_10$resample
```

### 5-fold cv

```{r}
train_data_5 = trainControl(method = "cv", number = 5)

# Fit the 4-variables model that we discussed in previous lectures
model_caret_5 = 
  train(target_death_rate ~ log(pct_bach_deg25_over) + incidence_rate + pct_private_coverage + 
    percent_smoke, 
    data = cancer_reg_subset,
    trControl = train_data_5,
    method = 'lm',
    na.action = na.pass)

model_caret_5
```

```{r}
# Model coefficients

model_caret_5$finalModel

# Results of each fold

model_caret_5$resample
```
