---
title: "jy2947"
author: "Jiawei Ye"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('MASS') 
library(tidyverse)
library('glmnet')
library('reshape2')
library('ggplot2')
library('faraway')
```

#Literature review
[This](https://onlinelibrary.wiley.com/doi/full/10.1002/ijc.29210) article shows that cancer incidence and mortality rates differ in developing countries and developed countries. Mortality rates also differ for cancers at different sites. But we only have data for all cancer combined. 

[This](https://jamanetwork.com/journals/jama/fullarticle/2598772) article shows age-standardized mortality rate for neoplasms differs across counties in 2014. This article's model is using covariates pretty similar to what our dataset has.

*age-standardized mortality rate: The age-standardized mortality rate is a weighted average of the age-specific mortality rates per
100,000 persons, where the weights are the proportions of persons in the corresponding age
groups of the WHO standard population. WHO, [link](https://www.who.int/whosis/whostat2006AgeStandardizedDeathRates.pdf)

[This](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5376950/) article is saying mortality differs aross races. 


### Load Main dataset

```{r}
cancer_reg = read_csv("./data/Cancer_Registry.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(target_death_rate, everything()) %>%
  separate(geography, into = c("county", "state"), sep = ", ") %>% 
  mutate(
    avg_deaths_per_year = as.numeric(avg_deaths_per_year),
    med_income = as.numeric(med_income),
    pop_est2015 = as.numeric(med_income),
    county = str_replace(county, " ", ""),
    log_med_income = log(med_income))
```

### Add Smoking Pravalence (current/previous smokers)

* Lung cancer account for highest proportion of cancer deaths. ~20% of lung cancer patients have never smoked. Smoking prevalence within a state is important indicator for mortality. 
```{r}
tobacco_2013 = read_csv(file = "./data/BRFD_tobacco_2010_present.csv") %>% 
  janitor::clean_names() %>% 
  filter(response == "Never", year == "2013", gender == "Overall") %>% 
  dplyr::select(year = "year", state = "location_desc", response, percent_never = "data_value") %>%
  mutate(
    percent_smoke = as.numeric(100 - percent_never),
    year = as.numeric(year)) %>% 
  dplyr::select(state, percent_smoke) %>% 
  filter(state != c("Guam", "National Median (States and DC)", "Puerto Rico"))

# join data on smoking prevalence by state
cancer_reg = left_join(cancer_reg, tobacco_2013, by = "state") %>% 
  dplyr::select(target_death_rate, state, county, percent_smoke, everything())

# smoking prevalence for 50 states and district of columbia
cancer_reg %>% 
  distinct(state, percent_smoke)
```

### Model Building, Based on Subset

```{r}
# select(-county, -state) %>%
# variables based on tidying steps
cancer_reg = cancer_reg %>% 
  mutate(mortality = avg_deaths_per_year/pop_est2015, prevalence = avg_ann_count/pop_est2015) %>%
  dplyr::select(-pop_est2015, -avg_ann_count, -avg_deaths_per_year) %>%
  mutate(study_per_cap =  
        as.factor(ifelse(study_per_cap == 0, "none", 
                         ifelse(study_per_cap < quantile(study_per_cap, .25), "low",
                         ifelse(study_per_cap < quantile(study_per_cap, .5), "medium" ,
                         ifelse(study_per_cap < quantile(study_per_cap, .75), "high", "very high")))))) %>%
  mutate(pct_non_white = pct_black+ pct_asian + pct_other_race) %>%
  dplyr::select(-pct_black, -pct_asian, -pct_other_race)

# subset based on Apoorva's selection & smoke variable
# remove state & county
cancer_reg_subset = cancer_reg %>%
  dplyr::select(
    target_death_rate, percent_smoke, incidence_rate, med_income, median_age_male, median_age_female, pct_hs18_24,
    pct_bach_deg25_over, pct_employed16_over, pct_unemployed16_over, pct_public_coverage_alone, birth_rate, mortality, prevalence,
    pct_private_coverage, pct_emp_priv_coverage, pct_public_coverage)
```

### Final Model Recommend

Adjusted R-squared:  0.4935

**4 predictor model:** target_death_rate ~ log(pct_bach_deg25_over), incidence_rate, pct_private_coverage, percent_smoke

```{r}
fit_parsimony = lm(target_death_rate ~ log(pct_bach_deg25_over) + incidence_rate + pct_private_coverage + 
    percent_smoke, data = cancer_reg_subset)

summary(fit_parsimony)
```

### Ridge
```{r}
grid = 10^seq(5,-2, length=100)
ridge_cancer = lm.ridge(target_death_rate ~log(pct_bach_deg25_over) + incidence_rate + pct_private_coverage + 
    percent_smoke, data = cancer_reg_subset, lambda = grid)
dim(coef(ridge_cancer))

#coef for 10^5
coef(ridge_cancer)[1,]

# coeffcients for 10^-2
coef(ridge_cancer)[100,]
```

```{r}
response = 
  cancer_reg_subset %>% 
  dplyr::select(target_death_rate, pct_bach_deg25_over, incidence_rate, pct_private_coverage, percent_smoke) %>% 
  drop_na() %>% 
  dplyr::select(target_death_rate) %>% 
  as.matrix()

predictors = 
  cancer_reg_subset %>% 
  dplyr::select(target_death_rate, pct_bach_deg25_over, incidence_rate, pct_private_coverage, percent_smoke) %>% 
  drop_na() %>% 
  dplyr::select(-target_death_rate) %>% 
  as.matrix()

ridge_cancer_1 = glmnet(predictors, response, alpha = 0, lambda = grid)
dim(coef(ridge_cancer_1))

ridge_cancer_1$lambda[50] 
coef(ridge_cancer_1)[,50]
```
###Ridge CV
```{r}

set.seed(1)

cancer_train = sample(1:nrow(predictors),nrow(predictors)/2)

cancer_test = (-cancer_train)

response_test = response[cancer_test]


# Use build-in CV function; performs a 10-fold validation by default
# glmnet() generates it's own lambda sequence

set.seed(2)
cv_out = cv.glmnet(predictors[cancer_train,], response[cancer_train], alpha=0)
plot(cv_out)


# cv.glmnet() object contains the mean cross-validation error (cvm),
# lambda min that gives the minimum cvm, etc.
cv_out
best_lambda = cv_out$lambda.min
best_lambda       


# Re-fit the model with the min lambda value, look at the coeff and MSE
#ridge_pred = predict(ridge.cv, s=best_lambda, new_pred = predictors[cancer_test,])
#mean((ridge_pred - response_test)^2)


# Ridge regression using all observations and 'best' lambda
ridge_pred = glmnet(predictors, response, alpha = 0, lambda = best_lambda)

#Compare LS method and ridge
compare_ridge_ls = cbind(coef(fit_parsimony), coef(ridge_pred))
colnames(compare_ridge_ls) <- c("LS", "Ridge")
compare_ridge_ls
```

