---
title: "Model_jh4054"
author: "Joy Hsu"
date: "12/7/2018"
output: 
    html_document:
      toc: true
      toc_float: true
      toc_depth: 6
      code_folding: show
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE,
  warning = FALSE)

library(tidyverse)
library(HH) # For VIF function # or use car::vif(fit_rs)
library(leaps) # Stepwise and test-based criteria
library(modelr) # add predictions and cross-validation
```

### Load Main dataset

```{r}
cancer_reg = read_csv("./data/Cancer_Registry.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(target_death_rate, everything()) %>%
  separate(geography, into = c("county", "state"), sep = ", ") %>% 
  mutate(
    avg_deaths_per_year = as.numeric(avg_deaths_per_year),
    med_income = as.numeric(med_income),
    pop_est2015 = as.numeric(med_income),
    county = str_replace(county, " ", ""))
```

### 1. Remove Categorical and high proportion missing values

* Remove state and county - catergorical parameters related to observations
* Remove avg_ann_count and avg_deaths_per_year, since this data is already captured in mortality rate and incidence, weighted by county population. 
* Remove variables with high percentage missing values:
    * pct_employed16_over - 152 missing. This variable has some collinearity with pct_unemployed16_over (R = -0.65), so we are not completely excluding information related to employment. 
    * pct_some_col18_24 - 2285 missing. Over 2/3 missing values.
    * pct_private_coverage_alone - 609 missing. Since this variable has strong collinearity with pct_private_coverage (R = 0.93), so we are not excluding valuable information on insurance coverage

```{r}
# Examine missing values
# 3 variables with high missing: values pct_employed16_over (152), pct_some_col18_24 (2285), pct_private_coverage_alone (609)
skimr::skim(cancer_reg)

# observe collinearity between pct_private_coverage and variable to exclude, pct_private_coverage_alone
cancer_reg %>% 
  dplyr::select(target_death_rate, pct_private_coverage, pct_private_coverage_alone) %>% cor(x = ., use = "pairwise.complete.obs")

# observe collinearity between pct_unemployed16_over and variable to exclude, pct_employed16_over
cancer_reg %>% 
  dplyr::select(target_death_rate, pct_unemployed16_over, pct_employed16_over) %>% cor(x = ., use = "pairwise.complete.obs")

# remove variables with high missing values, county and state
cancer_reg_tidy = cancer_reg %>% 
  dplyr::select(-pct_employed16_over, -pct_some_col18_24, -pct_private_coverage_alone, -county, -state, -avg_ann_count, -avg_deaths_per_year)
```

### 2. Remove Variables with high Collinearity

Next, we will examine collinearity between remaining variables. Remove the following:

* get rid of bin_income, since we will use med_income to look at income
* med_income - CL with pct_bach_deg25_over
* pop_est2015 - CL with poverty_percent (-0.79)
* poverty_percent - CL with pct_public_coverage_alone (0.798)
* percent_married - CL with pct_married_households (0.87)
* pct_hs25_over - CL with pct_bach_deg25_over (-0.74)
* Only keep "pct_public_coverage_alone" - out of all insurance variables, this has highest correlation with main outcome. High CL between between all insurance variables. 

Other variables of consideration.
* pct_white and pct_black has high CL (-0.83), but from a demographic standpoint, we may be interested in keeping both. 
* create pct_nonwhite as a proxy
* discuss why pct_black and pct_white has such negative correlation in report

We are left with 20 variables
```{r}
# Examine collinearity between variables
cor_df = cancer_reg_tidy %>%
  dplyr::select(-binned_inc) %>% 
  cor()

# remove collinear variables
# remove variables due to missing values
# remove variables due to collinearity
# create proxy variable pct_nonwhite
cancer_reg_tidy = cancer_reg %>% 
  dplyr::select(
    -pct_employed16_over, -pct_some_col18_24, -pct_private_coverage_alone, -county, -state, -avg_ann_count, -avg_deaths_per_year) %>%  
  dplyr::select(
    -med_income, -median_age_female, -pct_emp_priv_coverage, -pct_public_coverage, -pct_private_coverage, -pop_est2015, -poverty_percent, -pct_hs25_over, -binned_inc) %>% 
  mutate(pct_nonwhite = 1 - pct_white)

skimr::skim(cancer_reg_tidy)
```

### 3. Variables to Transform IGNORE FOR NOW

1) med_income, poverty_percent. Keep *poverty_percent*, stronger linear rel with explanatory variable

```{r}
# scatterplot b/w variables
cancer_reg %>% 
  ggplot(aes(x = pct_white, y = log(target_death_rate))) +
  geom_point()
```

### 3. Automatic Search Procedures

Stepwise regression uses the AIC criterion for variable selection. Given a set of candidate models for the data, we prefer the model with the minimum AIC value. AIC rewards goodness of fit (as assessed by the likelihood function), but AIC also includes a penalty that is a function of number of parameters. 

```{r}
# define full and null sets for forward, backward, both ways search procedures
null = lm(target_death_rate ~ 1, data = cancer_reg_tidy)

full = lm(target_death_rate ~ ., data = cancer_reg_tidy)
```

**Forward Selection Model**
    
Step:  AIC=18143.45

11-Predictor Model(Adjusted R-squared:  0.5014): target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + percent_married + pct_unemployed16_over

```{r, warning=TRUE, error=TRUE}
# stepwise regression, forward
step(null, scope = list(lower = null, upper = full), direction = "forward")

# forward fit
fit_forward = lm(target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + 
    pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + percent_married + pct_unemployed16_over, data = cancer_reg_tidy)

summary(fit_forward)
```

**Backward Elimination Model**

Step:  AIC=18143.45

11-Predictor Model(Adjusted R-squared:  0.5014): target_death_rate ~ incidence_rate + median_age_male + percent_married + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_white + pct_other_race + pct_married_households + birth_rate

```{r, error=TRUE}
# stepwise regression, backward
step(full, data = cancer_reg_tidy, direction="backward")

# backward fit
fit_back = lm(target_death_rate ~ incidence_rate + median_age_male + percent_married + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_white + pct_other_race + pct_married_households + birth_rate, data = cancer_reg_tidy)

summary(fit_back)
```

**Stepwise Regression, Both Directions**

Same output as others

Step:  AIC=18143.45

11-Predictor Model(Adjusted R-squared:  0.5014): target_death_rate ~ incidence_rate + median_age_male + percent_married + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_white + pct_other_race + pct_married_households + birth_rate

```{r}
# stepwise regression, both directions
step(null, scope = list(upper=full), data = cancer_reg_tidy, direction = "both")

fit_both_dir = lm(target_death_rate ~ incidence_rate + median_age_male + percent_married + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_white + pct_other_race + pct_married_households + birth_rate, data = cancer_reg_tidy)

summary(fit_both_dir)
```

**Conclusion**

Automatic Search Procedures using forward & backward selection, stepwise regression generated the same "best model" with 12-parameters, using the AIC criterion. The model has Adjusted R-squared:  0.5014. 

### 4. Criterion Based Procedures

**Best subsets regression procedure with Mallows’ Cp and Adjusted R2 Criterion**

* For Mallow's Cp-statistic, the Cp Statistic should be less than or equal to the # of parameters. Optimizing for lowest Cp Statistic, we select 10 parameters.
* For R^2(adj) criteria, we optimize for highest R^2(adj), while accounting for parsimony. Selecting ~8 parameters optimizes both the R^2(adj) criterion and overarching goal for parsimony. Not much improvement over 8 parameters. 

```{r}
criterion = leaps::regsubsets(target_death_rate ~ ., data = cancer_reg_tidy, nvmax = 19)
crit_sum = summary(criterion)
summary(criterion)

# Plots for Cp Statistic and Adjusted R2
par(mar = c(4,4,1,1))
par(mfrow = c(1,2))

# Cp Statistic Plot 
plot(x = 1:18, y = crit_sum$cp, xlab = "No of parameters", ylab = "Cp Statistic")
# abline - adds straight lines to a plot
abline(0,1)

# Adjusted R2 Plot
plot(x = 1:18, y = crit_sum$adjr2, xlab = "No of parameters", ylab = "Adj R2")
```

**Summary Table for Cp Statistic and Adjusted R2**
```{r}
# fit with all parameters
fit_multi = lm(target_death_rate ~ ., data = cancer_reg_tidy)

# best subset of variables for given number of parameters
best = function(model, ...) {

  subsets <- regsubsets(formula(model), nvmax = 20, model.frame(model), ...)
  subsets <- with(summary(subsets), cbind(p = as.numeric(rownames(which)), which, rss, rsq, adjr2, cp, bic))
  
  return(subsets)
}  

# Select the 'best' model of all subsets for 8-predictor model
cp_r2_df = round(best(fit_multi, nbest = 1), 19)
cp_r2_df
```

The adj R2 looks pretty good for ~7 predictor models (0.49), but the Cp Criteria is too high (55.99)
```{r}
# should take log for pct_bach_deg25_over variable
cancer_reg_tidy %>% 
  ggplot(aes(x = log(pct_bach_deg25_over), y = target_death_rate)) +
  geom_point()
```

### 5. Final Model Recommend

**12-predictor Model (Adjusted R-squared:  0.5096):** target_death_rate ~ pct_bach_deg25_over + incidence_rate + binned_inc + pct_married_households + pct_hs18_24 + pct_other_race + median_age_male + birth_rate + pct_public_coverage_alone + percent_married + pct_unemployed16_over + pct_white

```{r}
fit_final = lm(target_death_rate ~ pct_bach_deg25_over + incidence_rate + binned_inc + pct_married_households + pct_hs18_24 + pct_other_race + median_age_male + birth_rate + pct_public_coverage_alone + percent_married + pct_unemployed16_over + pct_white, data = cancer_reg_tidy)

summary(fit_final)
```



