---
title: "model2_cv"
author: "Xinyi Lin"
date: "12/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE,
  warning = FALSE)

library(tidyverse)
library(HH) # For VIF function # or use car::vif(fit_rs)
library("leaps") # Stepwise and test-based criteria
library(modelr) # add predictions and cross-validation
library(caret)
```

### Load Main dataset

```{r}
cancer_reg = read_csv("./data/Cancer_Registry.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(target_death_rate, everything()) %>%
  separate(geography, into = c("county", "state"), sep = ", ") %>% 
  mutate(
    avg_deaths_per_year = as.numeric(avg_deaths_per_year),
    med_income = as.numeric(med_income),
    pop_est2015 = as.numeric(med_income),
    county = str_replace(county, " ", ""))
```

### 1. Remove Categorical and high proportion missing values

* Remove state and county - catergorical parameters related to observations
* Remove avg_ann_count and avg_deaths_per_year, since this data is already captured in mortality rate and incidence, weighted by county population. 
* Remove variables with high percentage missing values:
    * pct_employed16_over - 152 missing. This variable has some collinearity with pct_unemployed16_over (R = -0.65), so we are not completely excluding information related to employment. 
    * pct_some_col18_24 - 2285 missing. Over 2/3 missing values.
    * pct_private_coverage_alone - 609 missing. Since this variable has strong collinearity with pct_private_coverage (R = 0.93), so we are not excluding valuable information on insurance coverage

```{r}
# Examine missing values
# 3 variables with high missing: values pct_employed16_over (152), pct_some_col18_24 (2285), pct_private_coverage_alone (609)
skimr::skim(cancer_reg)

# observe collinearity between pct_private_coverage and variable to exclude, pct_private_coverage_alone
cancer_reg %>% 
  dplyr::select(target_death_rate, pct_private_coverage, pct_private_coverage_alone) %>% cor(x = ., use = "pairwise.complete.obs")

# observe collinearity between pct_unemployed16_over and variable to exclude, pct_employed16_over
cancer_reg %>% 
  dplyr::select(target_death_rate, pct_unemployed16_over, pct_employed16_over) %>% cor(x = ., use = "pairwise.complete.obs")

# remove variables with high missing values, county and state
cancer_reg_tidy = cancer_reg %>% 
  dplyr::select(-pct_employed16_over, -pct_some_col18_24, -pct_private_coverage_alone, -county, -state, -avg_ann_count, -avg_deaths_per_year)
```

### 2. Remove Variables with high Collinearity

Next, we will examine collinearity between remaining variables. Remove the following:

* med_income - CL with pct_bach_deg25_over
* pop_est2015 - CL with poverty_percent (-0.79)
* poverty_percent - CL with pct_public_coverage_alone (0.798)
* percent_married - CL with pct_married_households (0.87)
* pct_hs25_over - CL with pct_bach_deg25_over (-0.74)
* Only keep "pct_public_coverage_alone" - out of all insurance variables, this has highest correlation with main outcome. High CL between between all insurance variables. 

Other variables of consideration.
* pct_white and pct_black has high CL (-0.83), but from a demographic standpoint, we may be interested in keeping both. 
* create pct_nonwhite as a proxy
* discuss why pct_black and pct_white has such negative correlation in report

We are left with 21 variables

```{r}
# Examine collinearity between variables
cor_df = cancer_reg_tidy %>%
  dplyr::select(-binned_inc) %>% 
  cor()

# remove collinear variables
# remove variables due to missing values
# remove variables due to collinearity
# create proxy variable pct_nonwhite
cancer_reg_tidy = cancer_reg %>% 
  dplyr::select(
    -pct_employed16_over, -pct_some_col18_24, -pct_private_coverage_alone, -county, -state, -avg_ann_count, -avg_deaths_per_year) %>%  
  dplyr::select(
    -med_income, -median_age_female, -pct_emp_priv_coverage, -pct_public_coverage, -pct_private_coverage, -pop_est2015, -poverty_percent, -pct_hs25_over, -percent_married, -binned_inc) %>% 
  mutate(pct_nonwhite = 1 - pct_white)

skimr::skim(cancer_reg_tidy)
```

### 3. Variables to Transform IGNORE FOR NOW

1) med_income, poverty_percent. Keep *poverty_percent*, stronger linear rel with explanatory variable

```{r}
# scatterplot b/w variables
cancer_reg %>% 
  ggplot(aes(x = pct_white, y = log(target_death_rate))) +
  geom_point()
```

### Model selection

### 1. Automatic Procedures

10-predictor Model:
Step:  AIC=18159.4
Adjusted R-squared:  0.4986
target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + 
    pct_other_race + pct_white + pct_hs18_24 + median_age_male + 
    birth_rate + pct_married_households + pct_unemployed16_over

### 2. Criterion Based Procedures

When using criterion based procedures, we get one models with 10 parameters satisfied Cp criterion best and models with 8 parameters satisfied adjusted r-square best.

10-parameters model: lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_other_race + pct_married_households + birth_rate, data = cancer_reg_tidy)

8-parameters model: lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_bach_deg25_over + pct_hs18_24 + pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_tidy)


```{r}
cancer_reg_cp =
  cancer_reg %>% 
  as.data.frame() %>% 
  dplyr::select(target_death_rate, pct_bach_deg25_over, incidence_rate, pct_married_households, pct_hs18_24, pct_other_race, median_age_male, birth_rate, pct_public_coverage_alone, percent_married, pct_unemployed16_over, pct_white)

leaps(x = cancer_reg_cp[,2:12], y = cancer_reg_cp[,1], nbest=1, method="Cp")
```

### Cross validation

```{r}
model_10 = lm(formula = target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + pct_unemployed16_over, data = cancer_reg_tidy)

model_9 = lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_other_race + pct_married_households + birth_rate, data = cancer_reg_tidy)

model_7 = lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_bach_deg25_over + pct_hs18_24 + pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_tidy)
```

### 1. 10-fold cv

```{r}
train_data_10 = trainControl(method = "cv", number = 10)

# Fit the 4-variables model that we discussed in previous lectures
model_caret10_10 = 
  train(target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + pct_unemployed16_over, 
    data = cancer_reg_tidy,
    trControl = train_data_10,
    method = 'lm',
    na.action = na.pass)

model_caret10_9 = 
  train(target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_other_race + pct_married_households + birth_rate, 
    data = cancer_reg_tidy,
    trControl = train_data_10,
    method = 'lm',
    na.action = na.pass)

model_caret10_7 = 
  train(target_death_rate ~ incidence_rate + median_age_male + pct_bach_deg25_over + pct_hs18_24 + pct_public_coverage_alone + pct_other_race + pct_married_households, 
    data = cancer_reg_tidy,
    trControl = train_data_10,
    method = 'lm',
    na.action = na.pass)

model_caret10_10 
#  RMSE     Rsquared   MAE     
#  19.7024  0.4938789  14.68475

model_caret10_9
#  RMSE      Rsquared   MAE     
#  19.68147  0.4967687  14.66503

model_caret10_7
#  RMSE      Rsquared   MAE     
#  19.79374  0.4900993  14.82677

```

### 1. 5-fold cv

```{r}
train_data_5 = trainControl(method = "cv", number = 5)

# Fit the 4-variables model that we discussed in previous lectures
model_caret5_10 = 
  train(target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + pct_unemployed16_over, 
    data = cancer_reg_tidy,
    trControl = train_data_5,
    method = 'lm',
    na.action = na.pass)

model_caret5_9 = 
  train(target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_other_race + pct_married_households + birth_rate, 
    data = cancer_reg_tidy,
    trControl = train_data_5,
    method = 'lm',
    na.action = na.pass)

model_caret5_7 = 
  train(target_death_rate ~ incidence_rate + median_age_male + pct_bach_deg25_over + pct_hs18_24 + pct_public_coverage_alone + pct_other_race + pct_married_households, 
    data = cancer_reg_tidy,
    trControl = train_data_5,
    method = 'lm',
    na.action = na.pass)

model_caret5_10 
#  RMSE      Rsquared   MAE     
#  19.70115  0.4967758  14.65786

model_caret5_9
#  RMSE      Rsquared   MAE     
#  19.69373  0.4956894  14.66347

model_caret5_7
#  RMSE      Rsquared   MAE     
#  19.82486  0.4890669  14.84762
```

Since three models have similar performance in cross validation, based on 'principle of parsimony', we chose models with 7 predictors.

Final model: `lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_tidy)`

### Model diagnostic for 4 predictors model
```{r}
par(mfrow = c(2, 2))
plot(model_7)
```

### Remove one outlier in y
```{r}
cancer_reg_remove = 
  cancer_reg_tidy %>% 
  filter(target_death_rate < 300)

model_remove = lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_remove)

summary(model_remove)

par(mfrow = c(2, 2))
plot(model_remove)
```

