---
title: "Model_jh4054"
author: "Joy Hsu, Xinyi Lin, Matt Parker, Apoorva Srinivasan, Jiawei Ye"
date: "12/7/2018"
output: 
    html_document:
      toc: true
      toc_float: true
      toc_depth: 6
      code_folding: show
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE,
  warning = FALSE)

library(tidyverse)
library(HH) # For VIF function # or use car::vif(fit_rs)
library(leaps) # Stepwise and test-based criteria
library(modelr) # add predictions and cross-validation
library(glmnet) # for ridge
```

### Load Main dataset

```{r}
cancer_reg = read_csv("./data/Cancer_Registry.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(target_death_rate, everything()) %>%
  separate(geography, into = c("county", "state"), sep = ", ") %>% 
  mutate(
    avg_deaths_per_year = as.numeric(avg_deaths_per_year),
    med_income = as.numeric(med_income),
    pop_est2015 = as.numeric(pop_est2015),
    county = str_replace(county, " ", "")) %>% 
  dplyr::select(state, county, everything()) %>% 
  arrange(target_death_rate, incidence_rate)
```

### 1. Remove Categorical and high proportion missing values

* Remove state and county - catergorical parameters related to observations
* Remove avg_ann_count and avg_deaths_per_year, since this data is already captured in mortality rate and incidence, weighted by county population. 
* Remove variables with high percentage missing values:
    * pct_employed16_over - 152 missing. This variable has some collinearity with pct_unemployed16_over (R = -0.65), so we are not completely excluding information related to employment. 
    * pct_some_col18_24 - 2285 missing. Over 2/3 missing values.
    * pct_private_coverage_alone - 609 missing. Since this variable has strong collinearity with pct_private_coverage (R = 0.93), so we are not excluding valuable information on insurance coverage

```{r}
# Examine missing values
# 3 variables with high missing: values pct_employed16_over (152), pct_some_col18_24 (2285), pct_private_coverage_alone (609)
skimr::skim(cancer_reg)

# observe collinearity between pct_private_coverage and variable to exclude, pct_private_coverage_alone
cancer_reg %>% 
  dplyr::select(target_death_rate, pct_private_coverage, pct_private_coverage_alone) %>% cor(x = ., use = "pairwise.complete.obs")

# observe collinearity between pct_unemployed16_over and variable to exclude, pct_employed16_over
cancer_reg %>% 
  dplyr::select(target_death_rate, pct_unemployed16_over, pct_employed16_over) %>% cor(x = ., use = "pairwise.complete.obs")

# remove variables with high missing values, county and state
cancer_reg_tidy = cancer_reg %>% 
  dplyr::select(-pct_employed16_over, -pct_some_col18_24, -pct_private_coverage_alone, -county, -state, -avg_ann_count, -avg_deaths_per_year)
```

### 2. Remove Variables with high Collinearity

Next, we will examine collinearity between remaining variables. Remove the following:

* remove bin_income, since we will use med_income to look at income
* remove poverty_percent, due to high collinearity with med_income (r = -0.78). We will use median income as key variable for model.
* remove of bin_income, since we will tentatively use med_income to look at income
* med_income - CL with multiple variables related to education attainment and insurance coverage: pct_bach_deg25_over, pct_private_coverage, pct_emp_priv_coverage, pct_public_coverage, pct_public_coverage_alone
* percent_married - CL with pct_married_households (r = 0.87)
* pct_hs25_over - CL with pct_bach_deg25_over (-0.74)
* Only keep "pct_public_coverage_alone" - out of all insurance status variables, this has highest correlation with main outcome. High CL between between all insurance variables. 

Other variables of consideration.
* pct_white and pct_black has high CL (-0.83), but from a demographic standpoint, we may be interested in keeping both. 
* create pct_nonwhite as a proxy
* discuss why pct_black and pct_white has such negative correlation in report

We are left with 21 variables
```{r}
# Examine collinearity between variables
cor_df = cancer_reg_tidy %>%
  dplyr::select(-binned_inc) %>% 
  cor()

# remove collinear variables
# remove variables due to missing values
# remove variables due to collinearity
# create proxy variable pct_nonwhite
cancer_reg_tidy = cancer_reg %>% 
  dplyr::select(
    -pct_employed16_over, -pct_some_col18_24, -pct_private_coverage_alone, -county, -state, -avg_ann_count, -avg_deaths_per_year) %>%  
  dplyr::select(
    -median_age_female, -pct_emp_priv_coverage, -pct_public_coverage, -pct_private_coverage, -poverty_percent, -pct_hs25_over, -percent_married, -binned_inc) %>% 
  mutate(pct_nonwhite = 1 - pct_white) %>% 
  arrange(target_death_rate, incidence_rate)

skimr::skim(cancer_reg_tidy)
```

### 3. Automatic Search Procedures

Stepwise regression uses the AIC criterion for variable selection. Given a set of candidate models for the data, we prefer the model with the minimum AIC value. AIC rewards goodness of fit (as assessed by the likelihood function), but AIC also includes a penalty that is a function of number of parameters. 

```{r}
# define full and null sets for forward, backward, both ways search procedures
null = lm(target_death_rate ~ 1, data = cancer_reg_tidy)

full = lm(target_death_rate ~ ., data = cancer_reg_tidy)
```

**Forward Selection Model**

Adjusted R-squared:  0.4988
Step:  AIC=18159.34
target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + 
    pct_other_race + pct_white + pct_hs18_24 + median_age_male + 
    birth_rate + pct_married_households + pct_unemployed16_over + 
    pop_est2015

```{r, warning=TRUE, error=TRUE}
# stepwise regression, forward
step(null, scope = list(lower = null, upper = full), direction = "forward")

# forward fit
fit_forward = lm(target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + 
    pct_other_race + pct_white + pct_hs18_24 + median_age_male + 
    birth_rate + pct_married_households + pct_unemployed16_over + 
    pop_est2015, data = cancer_reg_tidy)

summary(fit_forward)
car::vif(fit_forward)
```

**Backward Elimination Model**

Adjusted R-squared:  0.4988
Step:  AIC=18159.34
target_death_rate ~ incidence_rate + pop_est2015 + median_age_male + 
    pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + 
    pct_public_coverage_alone + pct_white + pct_other_race + 
    pct_married_households + birth_rate

```{r, error=TRUE}
# stepwise regression, backward
step(full, data = cancer_reg_tidy, direction = "backward")

# backward fit
fit_back = lm(target_death_rate ~ incidence_rate + pop_est2015 + median_age_male + 
    pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + 
    pct_public_coverage_alone + pct_white + pct_other_race + 
    pct_married_households + birth_rate, data = cancer_reg_tidy)

summary(fit_back)
car::vif(fit_back)
```

**Stepwise Regression, Both Directions**

Same 10 predictor output as forwards and backwards

Adjusted R-squared:  0.4988 
Step:  AIC=18159.34
target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + 
    pct_other_race + pct_white + pct_hs18_24 + median_age_male + 
    birth_rate + pct_married_households + pct_unemployed16_over + 
    pop_est2015

```{r}
# stepwise regression, both directions
step(null, scope = list(upper=full), data = cancer_reg_tidy, direction = "both")

fit_both_dir = lm(target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + pct_unemployed16_over + pop_est2015, data = cancer_reg_tidy)

summary(fit_both_dir)
car::vif(fit_both_dir)
```

**Conclusion**

Automatic Search Procedures using forward & backward selection, stepwise regression generated the same "best model" with 11-predictors, using the AIC criterion. The model has Adjusted R-squared: 0.4988. 

```{r}
fit_auto = lm(target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + pct_unemployed16_over + pop_est2015, data = cancer_reg_tidy)

summary(fit_auto)
```

### 4. Criterion Based Procedures

**Best subsets regression procedure with Mallows’ Cp and Adjusted R2 Criterion**

* For Mallow's Cp-statistic, the Cp Statistic should be less than or equal to the # of parameters. Optimizing for lowest Cp Statistic, we select 9 predictors
* For R^2(adj) criteria, we optimize for highest R^2(adj), while accounting for parsimony. Selecting ~7 predictors optimizes both the R^2(adj) criterion and overarching goal for parsimony.

```{r}
criterion = leaps::regsubsets(target_death_rate ~ ., data = cancer_reg_tidy, nvmax = 19)
crit_sum = summary(criterion)
summary(criterion)

# Plots for Cp Statistic and Adjusted R2
par(mar = c(4,4,1,1))
par(mfrow = c(1,2))

# Cp Statistic Plot 
plot(x = 1:19, y = crit_sum$cp, xlab = "No of parameters", ylab = "Cp Statistic")
# abline - adds straight lines to a plot
abline(0,1)

# Adjusted R2 Plot
plot(x = 1:19, y = crit_sum$adjr2, xlab = "No of parameters", ylab = "Adj R2")
```

**Summary Table for Cp Statistic and Adjusted R2**
```{r}
# fit with all parameters
fit_multi = lm(target_death_rate ~ ., data = cancer_reg_tidy)

# best subset of variables for given number of parameters
best = function(model, ...) {

  subsets <- regsubsets(formula(model), nvmax = 18, model.frame(model), ...)
  subsets <- with(summary(subsets), cbind(p = as.numeric(rownames(which)), which, rss, rsq, adjr2, cp, bic))
  
  return(subsets)
}  

# Select the 'best' model of all subsets for 8-predictor model
cp_r2_df = round(best(fit_multi, nbest = 1), digits = 3)
cp_r2_df
```

```{r}
# should take log for pct_bach_deg25_over variable
cancer_reg_tidy %>% 
  ggplot(aes(x = log(pct_bach_deg25_over), y = target_death_rate)) +
  geom_point()
```

### 5. Final 3 Models & Diagnostics (Check Model Assumptions)

Three models satisfied model assumptions: 

* normality of residuals
* equal variance

```{r}
# 10 predictor stepwise automatic search model
# Adjusted R-squared:  0.4986
fit_auto = lm(target_death_rate ~ log(pct_bach_deg25_over) + incidence_rate + pct_public_coverage_alone + 
    pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + pct_unemployed16_over, data = cancer_reg_tidy)

summary(fit_auto)
car::vif(fit_auto) 

par(mfrow = c(2,2))
plot(fit_auto)

##########
# 9 predictor cp model
# Adjusted R-squared:  0.4983 
fit_cp = lm(target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_other_race + pct_married_households + birth_rate, data = cancer_reg_tidy)

summary(fit_cp)
car::vif(fit_cp) # VIF values

par(mfrow = c(2,2))
plot(fit_cp)

##########
# 7 predictor adjusted R2 model
# Adjusted R-squared:  0.4927 
fit_r2 = lm(target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_tidy)

summary(fit_r2)
car::vif(fit_r2) # VIF values

# Diagnostic plots
par(mfrow = c(2,2))
plot(fit_r2)

#residual covariate plot
plot(cancer_reg_tidy$incidence_rate, fit_r2$residuals)
abline(h=0, lwd=2, col=2)
plot(cancer_reg_tidy$median_age_male, fit_r2$residuals)
abline(h=0, lwd=2, col=2)
plot(cancer_reg_tidy$pct_hs18_24, fit_r2$residuals)
abline(h=0, lwd=2, col=2)
plot(cancer_reg_tidy$pct_bach_deg25_over, fit_r2$residuals)
abline(h=0, lwd=2, col=2)
plot(cancer_reg_tidy$pct_public_coverage_alone, fit_r2$residuals)
abline(h=0, lwd=2, col=2)
plot(cancer_reg_tidy$pct_other_race, fit_r2$residuals)
abline(h=0, lwd=2, col=2)
plot(cancer_reg_tidy$pct_married_households, fit_r2$residuals)
abline(h=0, lwd=2, col=2)
```

### 6. Remove one outlier in y
```{r}
cancer_reg_remove = 
  cancer_reg_tidy %>% 
  filter(target_death_rate < 300)

model_remove = lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_remove)

summary(model_remove)

par(mfrow = c(2, 2))
plot(fit_r2)
```

### 6. Examine Leverage & Influential points

#### 6.1 **Outliers in Y - Studentized Residuals**

We use internally studentized residuals to quantify the magnitude of residuals in standard deviation unit. As a rule of thumb, an observation with |r~i~| > 2.5 may be considered an outlier in Y. 

The following points are extreme outliers in y with |r~i~| > 5.0:

* 802 - Williamsburg County, Virginia - NIH reported Incidence Rate for all cancers in Williamsburg County, Virginia, averaged across 2011-2015, is 376.2 per 100,000 (95% CI: 314.6, 447.3). However our dataset has incidence rate at 1014 per 100,000. **Steps**: exclude datapoint. Predicted mortality rate 265.0524, actual mortality rate it 162.1, residual -102.9524
* 3044 - Madison County, Mississippi
* 3046 - Woodson County, Kansas

```{r}
# add predictions & residuals for 7 predictor model to dataset
# df below used to examine state and county for outliers in y. 
cancer_reg_pred_resid = cancer_reg %>% 
  dplyr::select(
    state, county, target_death_rate, incidence_rate, median_age_male, pct_hs18_24, pct_bach_deg25_over, pct_private_coverage, pct_public_coverage_alone, pct_other_race, pct_married_households) %>% 
  modelr::add_predictions(fit_r2, var = "pred_model_7") %>% 
  modelr::add_residuals(fit_r2, var = "resid_model_7") %>% 
  arrange(target_death_rate, incidence_rate)

# rstandard function gives the INTERNALLY studentized residuals 
stu_res = rstandard(fit_r2)
# 68 points with student residuals > 2.5
stu_res[abs(stu_res) > 2.5]
# 3 points with student residuals > 5
stu_res[abs(stu_res) > 5]

# test remove point 802: Williamsburg County, Virginia
# no substantial change in coefficients. 
cancer_reg_remove = 
  cancer_reg_tidy %>% 
  filter(incidence_rate != 1014.2)

model_remove = lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_remove)

summary(model_remove)
```

#### 6.2 **Outliers in X - Leverage Values**

To determine outliers in X, we use leverage values (diagonal elements h~ii~ of the hat matrix) to measure how far each observation sits from the center of the X space. Observations with high leverage may have an influence on the fitted model's estimated coefficients. Observations with a leverage value 0.2 < h~ii~ < 0.5, will be considered moderate leverage observations. Examining the "hat" plot below, we do not observe any outliers in X. 
```{r}
# Obtain DFFITS, Cook's Distance, Hat diagonal elements.
influence_measures = influence.measures(fit_r2)

# plot of hat values and extract hat values above 0.2.
lev = hat(model.matrix(fit_r2))
plot(lev)
# command returns all observations with leverage values above 0.2
cancer_reg_tidy[lev > 0.2,]
```

#### 6.3 **Influential Points - Cook's Distance**

After identifying the outliers in Y (points 802, 3044, 3046), we will use Cook's distance measures to determine if they are influential. Applying **Cook's distance** criteria, an observation can be influential if it has a high residual and high h~ii~. As a rule of thumb, a D~i~ > 0.5 in R is of concern. Examination of the Cook's distance reveals that none of the y-outliers 802 (red), 3044 (blue), or 3046 (green) met the criteria as influential points. As such, we will not take further actions to remove Y outliers from our dataset. 

```{r}
# plot Cook's distance for fit_r2 7-predictor model 
cook = cooks.distance(fit_r2)
plot(cook,ylab = "Cooks distances")
points(802,cook[802],col = 'red')
points(3044,cook[3044],col = 'blue')
points(3046,cook[3046],col = 'green')
```

### 7. N-Fold Cross Validation & Violin Plots

```{r}
set.seed(20)
# create training and testing sets, 100 fold cross-validation, 80/20 split
cv_cm = modelr::crossv_mc(data = cancer_reg_tidy, n = 100, test = 0.2, id = "id")

# 
cv_cm = cv_cm %>% 
  mutate(lm_auto = map(train, ~lm(target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + pct_unemployed16_over, data = .x)),
         lm_cp = map(train, ~lm(target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_other_race + pct_married_households + birth_rate, data = .x)),
         lm_r2 = map(train, ~lm(target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_public_coverage_alone + pct_other_race + pct_married_households, data = .x))) %>% 
  mutate(rmse_auto = map2_dbl(lm_auto, test, ~rmse(model = .x, data = .y)),
         rmse_cp = map2_dbl(lm_cp, test, ~rmse(model = .x, data = .y)),
         rmse_r2 = map2_dbl(lm_r2, test, ~rmse(model = .x, data = .y)))
```

```{r}
# experimental values for RMSE will vary each time we rerun code
cv_cm %>% 
  dplyr::select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  group_by(model) %>% 
  summarise(mean_rmse = mean(rmse),
            var_rmse = var(rmse))

# Violin Plots
cv_cm %>% 
  dplyr::select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(
    model = str_replace(model, "rmse_", "model "),
    model = fct_reorder(model, rmse)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
    geom_violin() +
  labs(title = "Distribution of RMSE from Cross-Validation", 
    x = "Model", 
    y = "RMSE")
```

### 8. K-Fold Cross validation

```{r}
model_10 = lm(formula = target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + pct_unemployed16_over, data = cancer_reg_tidy)

model_9 = lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_other_race + pct_married_households + birth_rate, data = cancer_reg_tidy)

model_7 = lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_bach_deg25_over + pct_hs18_24 + pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_tidy)
```

### 8.1. 10-fold CV

```{r}
library(caret)
train_data_10 = caret::trainControl(method = "cv", number = 10)

# Fit the 4-variables model that we discussed in previous lectures
model_caret10_10 = 
  caret::train(target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + pct_unemployed16_over, 
    data = cancer_reg_tidy,
    trControl = train_data_10,
    method = 'lm',
    na.action = na.pass)

model_caret10_9 = 
  caret::train(target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_other_race + pct_married_households + birth_rate, 
    data = cancer_reg_tidy,
    trControl = train_data_10,
    method = 'lm',
    na.action = na.pass)

model_caret10_7 = 
  caret::train(target_death_rate ~ incidence_rate + median_age_male + pct_bach_deg25_over + pct_hs18_24 + pct_public_coverage_alone + pct_other_race + pct_married_households, 
    data = cancer_reg_tidy,
    trControl = train_data_10,
    method = 'lm',
    na.action = na.pass)

model_caret10_10 
#  RMSE     Rsquared   MAE     
#  19.7024  0.4938789  14.68475

model_caret10_9
#  RMSE      Rsquared   MAE     
#  19.68147  0.4967687  14.66503

model_caret10_7
#  RMSE      Rsquared   MAE     
#  19.79374  0.4900993  14.82677

```

### 8.2. 5-fold cv

```{r}
train_data_5 = caret::trainControl(method = "cv", number = 5)

# Fit the 4-variables model that we discussed in previous lectures
model_caret5_10 = 
  caret::train(target_death_rate ~ pct_bach_deg25_over + incidence_rate + pct_public_coverage_alone + pct_other_race + pct_white + pct_hs18_24 + median_age_male + birth_rate + pct_married_households + pct_unemployed16_over, 
    data = cancer_reg_tidy,
    trControl = train_data_5,
    method = 'lm',
    na.action = na.pass)

model_caret5_9 = 
  caret::train(target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_unemployed16_over + pct_public_coverage_alone + pct_other_race + pct_married_households + birth_rate, 
    data = cancer_reg_tidy,
    trControl = train_data_5,
    method = 'lm',
    na.action = na.pass)

model_caret5_7 = 
  caret::train(target_death_rate ~ incidence_rate + median_age_male + pct_bach_deg25_over + pct_hs18_24 + pct_public_coverage_alone + pct_other_race + pct_married_households, 
    data = cancer_reg_tidy,
    trControl = train_data_5,
    method = 'lm',
    na.action = na.pass)

model_caret5_10 
#  RMSE      Rsquared   MAE     
#  19.70115  0.4967758  14.65786

model_caret5_9
#  RMSE      Rsquared   MAE     
#  19.69373  0.4956894  14.66347

model_caret5_7
#  RMSE      Rsquared   MAE     
#  19.82486  0.4890669  14.84762
```

Since three models have similar performance in cross validation, based on 'principle of parsimony', we chose model with 7 predictors.

### 9. Ridge Regression
```{r}
grid = 10^seq(5,-2, length=100)
ridge_cancer = 
  lm.ridge(target_death_rate ~ incidence_rate + median_age_male + pct_bach_deg25_over + pct_hs18_24 +
               pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_tidy, lambda = grid)
dim(coef(ridge_cancer))

#coef for 10^5
coef(ridge_cancer)[1,]

# coeffcients for 10^-2
coef(ridge_cancer)[100,]
```

```{r}
response = 
  cancer_reg %>% 
  dplyr::select(target_death_rate, incidence_rate, median_age_male, pct_bach_deg25_over, pct_hs18_24, 
               pct_public_coverage_alone, pct_other_race, pct_married_households) %>% 
#  drop_na() %>% 
  dplyr::select(target_death_rate) %>% 
  as.matrix()

predictors = 
  cancer_reg %>% 
  dplyr::select(target_death_rate, incidence_rate, median_age_male, pct_bach_deg25_over, pct_hs18_24,
               pct_public_coverage_alone, pct_other_race, pct_married_households) %>% 
#  drop_na() %>% 
  dplyr::select(-target_death_rate) %>% 
  as.matrix()

ridge_cancer_1 = glmnet(predictors, response, alpha = 0, lambda = grid)
dim(coef(ridge_cancer_1))

ridge_cancer_1$lambda[50] 
coef(ridge_cancer_1)[,50]
```

### 9.1 Ridge Cross Validation

Cross validation was used to obtain the smallest lambda
```{r}

set.seed(1)

cancer_train = sample(1:nrow(predictors),nrow(predictors)/2)

cancer_test = (-cancer_train)

response_test = response[cancer_test]


# Use build-in CV function; performs a 10-fold validation by default
# glmnet() generates it's own lambda sequence

set.seed(2)
cv_out = cv.glmnet(predictors[cancer_train,], response[cancer_train], alpha=0)
plot(cv_out)

# cv.glmnet() object contains the mean cross-validation error (cvm),
# lambda min that gives the minimum cvm, etc.
cv_out
best_lambda = cv_out$lambda.min
best_lambda       

# Re-fit the model with the min lambda value, look at the coeff and MSE
# Ridge regression using all observations and 'best' lambda
ridge_pred = glmnet(predictors, response, alpha = 0, lambda = best_lambda)

#Compare LS method and ridge
compare_ridge_ls = cbind(coef(model_7), coef(ridge_pred))
colnames(compare_ridge_ls) <- c("LS", "Ridge")
compare_ridge_ls

```

### 10. Final Model

Final model: `lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_tidy)`

```{r}
fit_final = lm(formula = target_death_rate ~ incidence_rate + median_age_male + pct_hs18_24 + pct_bach_deg25_over + pct_public_coverage_alone + pct_other_race + pct_married_households, data = cancer_reg_tidy)

# Final Model Coefficients
fit_final %>% broom::tidy(conf.int = TRUE) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, std.error, p.value) %>% 
  rename(
    "beta1 estimates" = estimate, 
    "95% CI lower" = conf.low, 
    "95% CI upper" = conf.high) %>% 
  knitr::kable(digits = 3)
```

### 11. Supplementary Code

Supplementary code used to generate values for the report. 

```{r}
poverty_fit = lm(poverty_percent ~ pct_public_coverage_alone, data = cancer_reg)
summary(poverty_fit)

education_fit = lm(pct_hs18_24 ~ pct_bach_deg25_over, data = cancer_reg)
summary(education_fit)

insurance_fit = lm(pct_private_coverage ~ pct_public_coverage_alone, data = cancer_reg)
summary(insurance_fit)
```
